\documentclass{article}

% For submission
\usepackage[preprint]{neurips_2025}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}


\usepackage{float}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{graphicx}
\title{
    Computer Vision Final Project Report
}

\author{
    Ming Cheng \\
    23307130007
    \And
    Yifan Luo \\
    23307130031
}

\begin{document}

\maketitle

\begin{abstract}
This report presents two computer vision and embodied AI tasks.

The first task focuses on neural rendering and AIGC-based 3D reconstruction and generation, including real-world multi-view reconstruction, text-to-3D generation, single-image-to-3D generation, and scene fusion rendering. COLMAP, 2D Gaussian Splatting (2DGS), and the pre-trained DREAMFUSION-IF and Magic123 frameworks in threestudio are utilized to construct a complete 3D vision pipeline. After reconstruction, they were exported as textured meshes and then combined in Blender.

The second task investigates the zero-shot cross-environment generalization of Action Chunking with Transformers (ACT) on the CALVIN benchmark. Experimental results show that multi-environment training substantially improves robustness to visual distribution shifts, reducing the Action $L_1$ Error on an unseen environment by 15.7\% and increasing the rollout success rate from 0\% to 100\%. Furthermore, an ablation study demonstrates that moderate action horizons consistently yield the best performance.

\end{abstract}

\section*{Team Contribution}

This project was completed collaboratively by Yifan Luo and Ming Cheng. Both authors contributed to project discussion, experimental design, implementation, result analysis, and report writing.

\input{sections/Introduction.tex}

\input{sections/task1.tex}

\input{sections/task2.tex}

\appendix

\section{Project Resources}

\subsection{Task 1 Repository}

\url{https://github.com/F1shermanCNN/CV-Final-Task1}

\subsection{Task 1 Models, Blender Objects, and Rendering Videos}
\label{sec:models}
\url{https://drive.google.com/drive/folders/104ITdruMWy3bJy7J_qOayYOE7LNySR8B?usp=sharing}

\subsection{Task 2 Repository}

\url{https://github.com/Kevin-LD/lerobot-act-calvin}

\subsection{Task 2 Model Weights and Rollout Visualizations}

\url{https://drive.google.com/drive/folders/1UVtHY2a5legxZIZzB76gldc701c19pYH?usp=drive_link}

\subsection{Task 2 Complementary Dataset}

\url{https://huggingface.co/datasets/Kevin-LD/CALVIN_open_drawer/tree/main}

%\bibliographystyle{plainurl}
%\bibliographystyle{unsrt}
%\bibliography{refs.bib}

\end{document}
